Borel regularity for ODEs and Thimble Integrals

### 2024-02-09 exp-resurgence.tex
Brainstorm titles

% regular singular volterra operator
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
%%\newcommand{\kerwhole}{k}
\newcommand{\hardker}{k_0}
%%\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}
%%\newcommand{\roots}{\mathfrak{B}}

@@

\title{Borel regularity for ODEs and Thimble Integrals}
\author{Veronica Fantini and Aaron Fenyes}

@@

\begin{abstract}
    Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics. Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles. In addition, we give a geometric description of the Borel plane.
\end{abstract}
\tableofcontents
%
%
%
\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

@@

For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$. In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3. The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
and the perturbation
%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}). \]

Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
satisfies the equation $\solproto = \hardpart^\alpha \solproto$. We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve. This is equivalent to solving the inhomogeneous equation
\begin{equation}\label{eqn:inhomog-volterra}
\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
\end{equation}

The central idea of the proof is to show that $\solproto$ lies in $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, that $\softpart^\alpha$ maps $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough. It follows, by the Banach fixed point theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$. More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration. Starting with any initial guess $\solptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
\begin{align*}
\solptb^{(1)} & = \volterra^\alpha \solptb^{(0)} \\
\solptb^{(2)} & = \volterra^\alpha \solptb^{(1)} \\
\solptb^{(3)} & = \volterra^\alpha \solptb^{(2)} \\
& \;\;\vdots
\end{align*}
we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ to a solution.

@@

\end{proof}
\begin{lemma}\label{lem:formal-general-volterra}
The equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$ has a unique formal solution $\series{\psi}_\alpha$ in the affine subspace
\[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket \]
of the space $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
\end{lemma}
\begin{proof}
\textcolor{orange}{[Argument of Loday-Richaud\ldots]}
\end{proof}
\begin{proof}
Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}. Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}. Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.

@@

To prove Step $(b)$ we'll use the properties of the integral equation $\hat{\mathcal{P}}_\alpha\psi=0$. First, recall that ${\psi}_\alpha$ is the uniques solution of $\hat{\mathcal{P}}_\alpha\psi=0$ such that $\psi_\alpha\in\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ \cite[Theorem~4]{reg-sing-volterra}. Then, as shown in Lemma~\ref{lem:picard-power}, the Taylor expansion of $\psi_\alpha$ is the formal solution of $\hat{\mathcal{P}}_\alpha\psi=0$ in $\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$. Since by direct computations $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$
\[\tilde{\psi}_\alpha=\sum_{n=0}^\infty a_{\alpha,n}\frac{\zeta_\alpha^{n+\tau_\alpha-1}}{\Gamma(n+\tau_\alpha)},\]
our uniquess result ensures that $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$. Thus if $\hat{\psi}_\alpha$ denotes the sum of $\tilde{\psi}_\alpha$, we deduce that $\tilde{\psi}_\alpha\propto\psi_\alpha$.

@@

Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points. Let $I$ be the thimble integral 
\begin{equation}\label{exp-int}
I \defeq \int_{\Lambda_a^\theta} e^{-zf} \nu
\end{equation}
where $\Lambda_a^\theta$ is the thimble through the critical point $a$. In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular. The first step will be to rewrite $I$ as the Laplace transform of a function $\iota$ which is explicitly given by the\textit{thimble projection formula}.% \eqref{eqn:formula-proof}.   
\begin{lemma}\label{lem:thimble_proj_formula-proof}
\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota$ with $I = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
\begin{equation}\label{eqn:formula-proof}
    \iota = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right),
\end{equation}
where $\Lambda_\alpha^\theta(\zeta)$ is the part of $\Lambda_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$. Notice that $\Lambda_\alpha^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
\end{lemma}
\begin{proof}
    Let us recast the integral $I$ into the position domain. As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\Lambda_\alpha^\theta(\zeta)$ sweep backward along $\Lambda^-_\alpha(\zeta)$ and forward along $\Lambda^+_\alpha(\zeta)$, respectively. Hence, we have
\begin{align*}
I(z) & = \int_{\Lambda_a^\theta} e^{-zf} \nu \\
& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}\,d\zeta.
\end{align*}
Noticing that the right-hand side is a Laplace transform, we learn that
\begin{equation}\label{thimble-difference}
{\iota}(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}.
\end{equation}
\end{proof}
We'll now prove that $I$ is Borel regular:
\begin{theorem}\label{thm:maxim-proof}
If the integral defining $I$ is absolutely convergent, then $I$ is Borel regular. More explicitly: 
\begin{enumerate}
\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I$ is asymptotic to a trans-monomial $\tilde{I}\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item\label{part-2} The series $\tilde{I}$ is $1$-Gevrey. In other words, $\tilde{\iota} \defeq \borel_\zeta \tilde{I}$ converges near $\zeta=\alpha$.
\item\label{part-3} If you continue the sum of $\tilde{\iota}$ along the ray $\Gamma_\alpha^\theta$, and take its Laplace transform along that ray, you'll recover $I$.
\end{enumerate}
\end{theorem}
\begin{proof}
Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$. Let $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$ be the parts of $\Lambda_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively. We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$, respectively. \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
\[ \nu = \sum_{m \ge 0} b_m^a \tau^m\,d\tau \]
that converges in some disk $|\tau| < \varepsilon$.

>>>>

% regular singular volterra operator
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
%%\newcommand{\kerwhole}{k}
\newcommand{\hardker}{k_0}
%%\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}
\newcommand{\fmlsolwhole}{\series{f}}
\newcommand{\fmlsolproto}{\series{f}_0}
\newcommand{\fmlsolptb}{\series{f}_\star}
%%\newcommand{\roots}{\mathfrak{B}}

@@

\title{Borel regularity for ODEs and Thimble Integrals \\
\textcolor{Maroon}{Borel summation: new perspectives and examples (?)} \\
\color{Violet}Differential equations, thimble integrals, \\
and Borel summation as a regularization \\
\color{Tan} Borel summation as a regularization, and \\
the regularity of ODEs and thimble integrals \\
\color{CornflowerBlue} Borel summation as a regularization: \\
Borel regularity for ODEs and thimble integrals \\
\color{LimeGreen} The regularity of ODEs and thimble integrals \\
with respect to Borel summation}
\author{Veronica Fantini and Aaron Fenyes}

@@

\begin{abstract}
\textcolor{Violet}{Through Borel summation, one can often turn a formal solution of a problem into an analytic one. We take the perspective that the effectiveness of Borel summation is a regularity property}
    Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics. \textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles. In addition, we give a geometric description of the Borel plane.
\end{abstract}
\tableofcontents
%
%
%
\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

@@

For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$. In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3. The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
and the perturbation
%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]

Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
lies in the space $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$. We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve. This is equivalent to solving the inhomogeneous equation
\begin{equation}\label{eqn:inhomog-volterra}
\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
\end{equation}
The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough. It follows, by the contraction mapping theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$. More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration. Starting with any initial guess $\solptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
\begin{align*}
\solptb^{(1)} & = \volterra^\alpha \solptb^{(0)} \\
\solptb^{(2)} & = \volterra^\alpha \solptb^{(1)} \\
\solptb^{(3)} & = \volterra^\alpha \solptb^{(2)} \\
& \;\;\vdots
\end{align*}
we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ to a solution.

@@

\end{proof}
\textcolor{orange}{[We'll prove a formal analogue of Theorem~4 from \cite{reg-sing-volterra}. We use essentially the same technique]}, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ under \color{Tan}{the non-archimedean norm
\[ \big| c_n \zeta_\alpha^{\sigma+n} + c_{n+1} \zeta_\alpha^{\sigma+n+1} + c_{n+2} \zeta_\alpha^{\sigma+n+2} + \ldots \big|_\lambda = \lambda^{-(\sigma+n)} \]
\color{Maroon}
the weighted $L^1$ norm \textcolor{orange}{[whoops, not defined for all formal power series]}
\[ \big| c_n \zeta_\alpha^{\sigma+n} + c_{n+1} \zeta_\alpha^{\sigma+n+1} + c_{n+2} \zeta_\alpha^{\sigma+n+2} + \ldots \big|_\lambda = |c_n| \lambda^{-(\sigma+n)} + |c_{n+1}| \lambda^{-(\sigma+n+1)} + |c_{n+2}| \lambda^{\sigma+n+2} + \ldots\]
for some $\lambda > 1$. \textcolor{orange}{[My hope was to use a non-archimedean norm to give a contraction mapping theorem formulation of an argument that more and more terms match, but it's hard to split up the operator in a way that makes more and more terms match\ldots]}
\begin{lemma}\label{lem:formal-general-volterra}
The equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$ has a unique formal solution $\series{\psi}_\alpha$ in the affine subspace
\[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket \]
of the space $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
\end{lemma}
\begin{proof}
In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3. Instead of looking for an analytic solution, like we do in \cite{reg-sing-volterra}, we'll seek a formal solution $\fmlsolwhole$. First, we have to make sure the equation makes sense in the space of formal power series. Let $\series{p} = P(-\zeta)$ and $\series{q} = Q(-\zeta)$, thinking of the polynomials as formal power series, and let $\series{R}$ be the Taylor series of $R$. The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
\color{magenta}
\[ \hardpart^\alpha = -\tfrac{1}{\series{p}} \circ \partial^{-1}_{\zeta, \alpha} \circ \series{q} \]
\color{Maroon}
and the perturbation
\color{magenta}
\[ \softpart^\alpha = \tfrac{1}{\series{p}} \circ \partial^{-2}_{\zeta, \alpha} \circ \series{R}\big(\partial^{-1}_{\zeta, \alpha}\big), \]
[have to get a contraction somehow for this to work like I imagined] \color{Maroon} which are both written here as operators on $\C\llbracket \zeta_\alpha \rrbracket$.

Now, let's run through the proof of Theorem~3, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ in the ``$\lambda$-adic'' norms described above. For simplicity, we'll specialize the proof to the case we consider in Theorem~4. First, picking an arbitrary point $\zeta = \eta$ in $\Omega_\alpha$, we show that the {\em prototype solution}
%%\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
%%\[ \solproto = \frac{1}{\series{p}(a)} \exp\big(-\partial^{-1}_{\zeta, \eta} (\series{q}/\series{p})\big) \]
\[ \fmlsolproto = \frac{1}{\series{p}} \left(\frac{\zeta}{\eta}\right)^{\tau_\alpha} \exp\left[-\partial^{-1}_{\zeta, \eta} \left( \frac{\series{q}}{\series{p}} + \frac{\tau_\alpha}{\zeta} \right)\right] \]
satisfies the equation $\fmlsolproto = \hardpart^\alpha \fmlsolproto$. Our expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, gives a convergent power series expansion of the analytic prototype solution defined in \cite{reg-sing-volterra}.

This definition of the prototype solution is taken from an intermediate step of the calculate in Section~3.2.1 \textcolor{orange}{\tt sec:construction} of \cite{reg-sing-volterra}, in which

to express the prototype solution as a formal power series that satisfies the same equation. The definition of $\tau_\alpha$ ensures that $\series{q}/\series{p} + \tau_\alpha/\zeta$ is in $\C\llbracket \zeta_\alpha \rrbracket$, so $\fmlsolproto$ is in $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.

Next, we look for a perturbation $\fmlsolptb$ that makes $\fmlsolwhole = \fmlsolproto + \fmlsolptb$ a solution of the Volterra equation we're trying to solve. This is equivalent to solving the inhomogeneous equation
\begin{equation}\label{eqn:inhomog-volterra2}
\fmlsolptb = \softpart^\alpha \fmlsolproto + \volterra^\alpha \fmlsolptb
\end{equation}
The central idea of the proof is to show that $\softpart^\alpha$ maps $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket$ and that $\volterra^\alpha$ is a contraction of $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.

$\solproto$ lies in $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, that $\softpart^\alpha$ maps $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough. It follows, by the contraction mapping theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$. More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration. Starting with any initial guess $\fmlsolptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
\begin{align*}
\fmlsolptb^{(1)} & = \volterra^\alpha \fmlsolptb^{(0)} \\
\fmlsolptb^{(2)} & = \volterra^\alpha \fmlsolptb^{(1)} \\
\fmlsolptb^{(3)} & = \volterra^\alpha \fmlsolptb^{(2)} \\
& \;\;\vdots
\end{align*}
we get a sequence of functions that converges in $\zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket$ to a solution.

\textcolor{orange}{[Argument of Loday-Richaud\ldots]}
\end{proof}
\begin{proof}
Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}. Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}. Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.

@@

To prove Step $(b)$ we'll use the properties of the integral equation $\hat{\mathcal{P}}_\alpha\psi=0$. First, recall that ${\psi}_\alpha$ is the uniques solution of $\hat{\mathcal{P}}_\alpha\psi=0$ such that $\psi_\alpha\in\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ \cite[Theorem~4]{reg-sing-volterra}. Then, as shown in Lemma~\ref{lem:picard-power}, the Taylor expansion of $\psi_\alpha$ is the formal solution of $\hat{\mathcal{P}}_\alpha\psi=0$ in $\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$. Since by direct computations $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$
\[\tilde{\psi}_\alpha=\sum_{n=0}^\infty a_{\alpha,n}\frac{\zeta_\alpha^{n+\tau_\alpha-1}}{\Gamma(n+\tau_\alpha)},\]
our uniquess result ensures that $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$ in their common region of convergence. Thus if $\hat{\psi}_\alpha$ denotes the sum of $\tilde{\psi}_\alpha$, we deduce that $\tilde{\psi}_\alpha\propto\psi_\alpha$.

@@

Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points. Let $I$ be the thimble integral 
\begin{equation}\label{exp-int}
I \defeq \int_{\Lambda_a^\theta} e^{-zf} \nu
\end{equation}
where $\Lambda_a^\theta$ is the thimble through the critical point $a$. In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular. The first step will be to rewrite $I$ as the Laplace transform of a function $\iota$ which is explicitly given by the \textit{thimble projection formula}.% \eqref{eqn:formula-proof}.   
\begin{lemma}\label{lem:thimble_proj_formula-proof}
\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota$ with $I = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
\begin{equation}\label{eqn:formula-proof}
    \iota = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right),
\end{equation}
where $\Lambda_\alpha^\theta(\zeta)$ is the part of $\Lambda_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$. Notice that $\Lambda_\alpha^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
\end{lemma}
\begin{proof}
    Let us recast the integral $I$ into the position domain. As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\Lambda_\alpha^\theta(\zeta)$ sweep backward along $\Lambda^-_\alpha(\zeta)$ and forward along $\Lambda^+_\alpha(\zeta)$, respectively. Hence, we have
\begin{align*}
I(z) & = \int_{\Lambda_a^\theta} e^{-zf} \nu \\
& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}\,d\zeta.
\end{align*}
Noticing that the right-hand side is a Laplace transform, we learn that
\begin{equation}\label{thimble-difference}
{\iota}(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}.
\end{equation}
\end{proof}
We'll now prove that $I$ is Borel regular:
\begin{theorem}\label{thm:maxim-proof}
If the integral defining $I$ is absolutely convergent, then $I$ is Borel regular. More explicitly: 
\begin{enumerate}
\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I$ is asymptotic to a trans-monomial $\tilde{I}\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item\label{part-2} The series $\tilde{I}$ is $1$-Gevrey. In other words, $\tilde{\iota} \defeq \borel_\zeta \tilde{I}$ converges near $\zeta=\alpha$.
\item\label{part-3} If you continue the sum of $\tilde{\iota}$ along the ray $\Gamma_\alpha^\theta$, and take its Laplace transform along that ray, you'll recover $I$.
\end{enumerate}
\end{theorem}
\begin{proof}
Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$. Let $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$ be the parts of $\Lambda_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively. We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$, respectively. \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
\[ \nu = \sum_{m \ge 0} b_m^a \tau^m\,d\tau \]
that converges in some disk $|\tau| < \varepsilon$.
